Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-07-06 src/tex/ms.tex
Minor changes for B.3 & B.5

Equation \eqref{eq:waveform_modification} can be derived as the first order effect in an expansion away from \ac{GR} under multiple frameworks.
In general, $\kappa$ will be a function of the theory parameters and the cosmological history, e.g., the value of the pseudo-scalar field and its derivative in Chern-Simons gravity \cite{Alexander:2009tp}.
Since it originates from a truncated series expansion%
\footnote{Often the birefringent effect is written as an expansion in redshift, $z$ \cite[e.g.][]{Zhao:2019xmm}, rather than distance.  Here we use $d_C$ to emphasize that the effect accumulates \emph{per cycle}, or with propagation distance.  Thus, current ground-based experiments, which can detect gravitational waves to $z \simeq 1$, $d_C \simeq d_H$ (Hubble distance), are already observing propagation over a large fraction of the universe and constrain this effect meaningfully.}, %
Eq.~\eqref{eq:waveform_modification} is a good approximation only for small exponents, 
\begin{equation}
\left|\kappa\right| d_C \left(f/100\, \mathrm{Hz}\right) < 1\, .
\end{equation}
Otherwise, more frequency-dependent terms would enter the exponent of Eq.~\eqref{eq:waveform_modification} in a theory-dependent way.

@@

In this section, we present the results of our study.
We first show the $\kappa$ measurements from of all events in our set, as well as the resulting global measurement of $\kappa$ that represents our primary constraint on birefringence (Sec.~\ref{sec:results:gwtc}).
We then assess the collection of measurements in more detail through a hierarchical analysis (Sec.~\ref{sec:results:hier}).
Finally, we discuss some special events individually, and outline the degeneracies that arise between birefringence and orbital precession (Sec.~\ref{sec:results:notable}).

>>>>

Equation \eqref{eq:waveform_modification} can be derived as the first order effect in an expansion away from \ac{GR} under multiple frameworks.
In general, $\kappa$ will be a function of the theory parameters and the cosmological history, e.g., the value of the pseudo-scalar field and its derivative in Chern-Simons gravity \cite{Alexander:2009tp}.
Since it originates from a truncated series expansion%
\footnote{Often the birefringent effect is written as an expansion in redshift, $z$ \cite[e.g.][]{Zhao:2019xmm}, rather than distance.  Here we use $d_C$ to emphasize that the effect accumulates \emph{per cycle}, or with propagation distance.  Thus, current ground-based experiments, which can detect gravitational waves to $z \simeq 1$, $d_C \simeq d_H$ (Hubble distance), are already observing propagation over a large fraction of the universe and constrain this effect meaningfully.}, %
Eq.~\eqref{eq:waveform_modification} is a good approximation only for small exponents, 
\begin{equation}
\left|\kappa\right| d_C \left(f/100\, \mathrm{Hz}\right) < 1\,,
\end{equation}
note that $d_C$ is in units of Gpc.
Otherwise, more frequency-dependent terms would enter the exponent of Eq.~\eqref{eq:waveform_modification} in a theory-dependent way.

@@

In this section, we present the results of our study.
We first show the $\kappa$ measurements of all events in our set, as well as the resulting global measurement of $\kappa$ that represents our primary constraint on birefringence (Sec.~\ref{sec:results:gwtc}).
We then assess the collection of measurements in more detail through a hierarchical analysis (Sec.~\ref{sec:results:hier}).
Finally, we discuss some special events individually, and outline the degeneracies that arise between birefringence and orbital precession (Sec.~\ref{sec:results:notable}).
